\hypertarget{terms-and-definitions}{%
\section{Terms and Definitions}\label{terms-and-definitions}}
The following are the basic terms and definitions which are
used in Graph theory.
\hypertarget{some-basic-definitions}{%
\subsection{Some basic definitions:}\label{some-basic-definitions}}

\begin{itemize}
\item
  Vertices: A graph has vertices. Which can be understood as points.
\item
  Edge: An edge is an unordered pair of vertices.
\item
  V(G) is the vetex set of graph G.
\item
  E(G) is the edge set of graph G.
\item
  Degree of a vertex: deg(v). Number of edges connected to a vertex.
\item
  isolated vertex v: deg(v) = 0
\item
  End vertex w: deg(w) = 1
\end{itemize}

\hypertarget{some-basic-facts}{%
\subsection{Some basic facts}\label{some-basic-facts}}

\hypertarget{handshaking-lemma}{%
\subsubsection{Handshaking Lemma}\label{handshaking-lemma}}

In any graph the sum of all the the vertex-degree is an even number - in
fact, twice the number of edges, since each edge contributes exactly 2
to the sum. Total summation of is edes*2

\hypertarget{adjacency}{%
\subsubsection{Adjacency}\label{adjacency}}

Two vertices are adjacent if they have an edge between them. Two edges
are adjacent if they have a vertex in common.

\hypertarget{what-graphs-are-not-about}{%
\subsubsection{What graphs are not
about}\label{what-graphs-are-not-about}}

metrical properties: length and shape of the edges. (Irrelevant in graph
theory). (so if an edge is smaller , larger etc doesnt matter what
matters if the edges between two vertices are connected or not )

\hypertarget{some-more-definitions}{%
\subsubsection{Some more definitions}\label{some-more-definitions}}

\hypertarget{simple-graphs}{%
\paragraph{Simple graphs:}\label{simple-graphs}}

graphs with no loops and multiple edges.

\hypertarget{general-graph}{%
\paragraph{General graph:}\label{general-graph}}

loops and multiple edges are allowed.

\hypertarget{digraphs}{%
\paragraph{Digraphs:}\label{digraphs}}

Directed graphs. When edges have arrows.

\hypertarget{walk}{%
\paragraph{Walk:}\label{walk}}

A way of getting from one vertex to another, and consists of a sequence
of edges. P -\textgreater{} Q -\textgreater{} R is a walk of length 2

\hypertarget{path}{%
\paragraph{Path:}\label{path}}

A walk in which no vertex appears more than once.

\hypertarget{cycle}{%
\paragraph{Cycle}\label{cycle}}

A path like this: Q -\textgreater{} S -\textgreater{} T -\textgreater{}
Q is called a cycle.

\hypertarget{subgraph}{%
\paragraph{Subgraph}\label{subgraph}}

G - e is the graph obtained from G by deleting the edge e.

\hypertarget{adjecency-matrix}{%
\paragraph{Adjecency Matrix}\label{adjecency-matrix}}

If G is a graph with vertices labelled \{1,2,..n\}, its adjacency matrix
A is n * n matrix whose ijth entry is the number of edges joining vertex
i and vertex j.

\hypertarget{null-graph}{%
\paragraph{Null Graph}\label{null-graph}}

Edge set is empty. All vertices are isolated.

\hypertarget{complete-graph}{%
\paragraph{Complete Graph}\label{complete-graph}}

A simple graph in which each pair of distinct vertices are adjacent is a
complete. Complete Graph of n vertices are denoted as Kn. They have
n(n-1)/2 edges.

\hypertarget{cycle-graphs}{%
\paragraph{Cycle Graphs}\label{cycle-graphs}}

A connected graph which is regular of degree 2. A cycle graph of n
vertices is denoted by Cn.

\hypertarget{path-graph}{%
\paragraph{Path Graph}\label{path-graph}}

A graph obtained from Cn by removing an edge. Denoted by Pn.

\hypertarget{wheel}{%
\paragraph{Wheel}\label{wheel}}

The graph obtained from Cn-1 by joining each vertex to a new vertex v is
wheel on n vertices, denoted by Wn.

\hypertarget{regular-graph}{%
\paragraph{Regular Graph}\label{regular-graph}}

Each vertex has the same degree. With that degree r, the graph is a
regular of degree r of r-regular.

\hypertarget{bipartite-graph}{%
\paragraph{Bipartite Graph}\label{bipartite-graph}}

If the vertex set of a graph G can be split into two disjoint sets A and
B such that each edge of G joins a vertex of A and a vertex of B, then G
is a bipartite graph. (like when we divide it into two sets anything in
a will connect with set b not another set of a)

\hypertarget{hamiltonian-graphs}{%
\paragraph{Hamiltonian graphs}\label{hamiltonian-graphs}}

Graphs containing walks that include every vertex exactly once, ending
at initial vertex. ( so we should start and end in same point without
repeating vertices not all vertices have to be used )
